### 2018-09-27 paper.tex
Wip

>>>>

While models may be represented in part by traditional installable
software---e.g. a TensorFlow program that imperatively defines a model
graph structure when run---models require more to be construed as
reusable code: \emph{models must be trainable on novel data}.

Table \ref{software-vs-models} compares traditional software with
reusable models.

\begin{table}[h!]
  \begin{center}
    \caption{Traditional software vs reusable models.}
    \label{software-vs-models}
    \begin{tabular}{l|l}
      Traditional software & Installed code
      Reusable models & Installed code + trainable on novel data
    \end{tabular}
  \end{center}
\end{table}

The remainder of this paper will outline an approach to package
management applied to machine learning models that incorporates
\emph{model operations} and \emph{run management} as a central enabler
of model code reuse.
